Quotient maps and configuration spaces of hard disks

### 2022-02-10 manuscript/main.tex
eq.4 alignment fixed
eq 4 numbering updated

All other quotient spaces are initially embedded in an infinite-dimensional descriptor space, and a numerical approach is used to estimate the minimum number of descriptors necessary to maintain the embedding. \red{This idea is analogous to representing a function in the Fourier space, but using a finite subset of infinitely-many coefficients.} Given a configuration space of $n$ disks, the distribution $f$ is defined as a sum of Dirac-delta distributions $\delta(\vec{a}_j)$ located at the disk centers $\vec{a}_j$ in the $a_1a_2$-coordinate system in Fig.\ \ref{fig:figure2}, or
\begin{equation}
f(\vec{a}) = \sum_{j = 1}^{n} \delta(\vec{a}_j) = \sum_{\vec{k}} {c_{\vec{k}} \exp{(2\pi \rmi \vec{k} \cdot \vec{a})}}
\label{eq:f}
\end{equation}
where $c_{\vec{k}}$ are the complex coefficients of the reciprocal lattice expansion and $\vec{k} = [p, q]$ for integers $p$ and $q$. The infinite set of $c_{\vec{k}}$ can be calculated using the orthogonality of the complex exponentials as
\begin{equation}
c_{\vec{k}} = \sum_{j=1}^{n} \exp{(-2\pi \rmi \vec{k} \cdot \vec{a}_j)} .
\label{eq:c_k}
\end{equation}
$c_{\vec{k}}$ respects the periodicity of the lattice and is invariant to permutations of the disk labels due to the commutative property of the summation in Eq.\ \ref{eq:f}. It can be shown that translating a configuration (by adding an offset to the $\vec{a}_j$) only changes the phase of the coefficients. This means that the moduli of the coefficients, or
\begin{equation}
z_{\vec{k}} = \sqrt{c^\ast_{\vec{k}} c_{\vec{k}}}
\label{eq:z_k}
\end{equation}
where $^\ast$ denotes the complex conjugate, are a set of real-valued descriptors that are invariant to disk label permutations and rigid translations. Observe that the descriptors $z_{\vec{k}}$ also respect inversion symmetry. Numerical experiments indicate that the rank of the Jacobian of the map from the $\vec{a}_j$ to the $z_{\vec{k}}$ is generically $2(n - 1)$, suggesting that some number of these descriptors could be sufficient to construct an embedding of $\Lambda / \mathcal{S}_2$.

>>>>

All other quotient spaces are initially embedded in an infinite-dimensional descriptor space, and a numerical approach is used to estimate the minimum number of descriptors necessary to maintain the embedding. \red{This idea is analogous to representing a function in the Fourier space, but using a finite subset of infinitely-many coefficients.} Given a configuration space of $n$ disks, the distribution $f$ is defined as a sum of Dirac-delta distributions $\delta(\vec{a}_j)$ located at the disk centers $\vec{a}_j$ in the $a_1a_2$-coordinate system in Fig.\ \ref{fig:figure2}, or
\begin{subequations}
	\begin{align}
	f(\vec{a}) 	&= \sum_{j = 1}^{n} \delta(\vec{a}_j) \\ 
				&= \sum_{\vec{k}} {c_{\vec{k}} \exp{(2\pi \rmi \vec{k} \cdot \vec{a})}}
	\label{eq:f}
	\end{align}
\end{subequations}
where $c_{\vec{k}}$ are the complex coefficients of the reciprocal lattice expansion and $\vec{k} = [p, q]$ for integers $p$ and $q$. The infinite set of $c_{\vec{k}}$ can be calculated using the orthogonality of the complex exponentials as
\begin{equation}
c_{\vec{k}} = \sum_{j=1}^{n} \exp{(-2\pi \rmi \vec{k} \cdot \vec{a}_j)} .
\label{eq:c_k}
\end{equation}
$c_{\vec{k}}$ respects the periodicity of the lattice and is invariant to permutations of the disk labels due to the commutative property of the summation in Eq.\ \ref{eq:f}. It can be shown that translating a configuration (by adding an offset to the $\vec{a}_j$) only changes the phase of the coefficients. This means that the moduli of the coefficients, or
\begin{equation}
z_{\vec{k}} = \sqrt{c^\ast_{\vec{k}} c_{\vec{k}}}
\label{eq:z_k}
\end{equation}
where $^\ast$ denotes the complex conjugate, are a set of real-valued descriptors that are invariant to disk label permutations and rigid translations. Observe that the descriptors $z_{\vec{k}}$ also respect inversion symmetry. Numerical experiments indicate that the rank of the Jacobian of the map from the $\vec{a}_j$ to the $z_{\vec{k}}$ is generically $2(n - 1)$, suggesting that some number of these descriptors could be sufficient to construct an embedding of $\Lambda / \mathcal{S}_2$.
